Publication Ready

### 2023-02-11 Articles.Rmd
updated plots after adding MSE for MLE in rmarkdown files

# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE
RS_ACC<-Accuracy_Data

@@

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_ACC<-All_ACC

@@

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(RS_ACC,OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Average MSE Y",
                                        All_ACC))

@@

# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

@@

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_ACC<-Accuracy_Data

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Average MSE Y",
                                        All_ACC))

@@

# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

@@

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Average MSE Y",
                                        All_ACC))

@@

# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

@@

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE",All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Average MSE Y",All_ACC))

@@

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")

@@

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggsave(filename = "SMSE_MI_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggsave(filename = "SMSE_MI_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "ACCURACY_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggsave(filename = "ACCURACY_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
```

>>>>

# Random Sampling
load(here("Non_Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE
RS_MSE_MLE<-All_MSE_MLE
RS_ACC<-Accuracy_Data

@@

# OSMAC
load(here("Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-All_ACC

@@

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(RS_MSE_MLE,OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(RS_ACC,OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Average MSE Y",
                                        All_ACC))

@@

# Random Sampling
load(here("Non_Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

@@

# OSMAC
load(here("Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-Accuracy_Data

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Average MSE Y",
                                        All_ACC))

@@

# Random Sampling
load(here("Non_Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

@@

# OSMAC
load(here("Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Average MSE Y",
                                        All_ACC))

@@

# Random Sampling
load(here("Non_Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

@@

# OSMAC
load(here("Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE",All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE for MLE",All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Average MSE Y",All_ACC))

@@

Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p7

Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p8

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")

@@

ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggsave(filename = "SMSE_MI_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggsave(filename = "SMSE_MI_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "ACCURACY_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggsave(filename = "ACCURACY_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 12)

ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mMSE.eps",res=300,width = 12,height = 12)
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mVc.eps",res=300,width = 12,height = 12)
```

### 2023-02-11 Non_Identical_r0/Rmarkdown/Summary/r1_Best_Subsampling_Method.Rmd
updated plots after adding MSE for MLE in rmarkdown files

# OSMAC
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))

@@

# OSMAC Model Free
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC_MF.RData"))

>>>>

# OSMAC
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC_r1.RData"))

@@

# OSMAC Model Free
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC_MF_r1.RData"))

### 2023-02-11 r1_Publication_Ready.Rmd
updated plots after adding MSE for MLE in rmarkdown files

# OSMAC
load(here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))

@@

```{r Identical r0 Plots with gg.gap,fig.height=4}
SS_Choice<-100*c(10:15)

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p1_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p2_New

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p3_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p4_New

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p5_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p6_New

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p7_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p8_New

```

```{r All Plots}
ggarrange(p1,p1_New,
          p2,p2_New,nrow = 4)

ggarrange(p5_New,p6_New,nrow = 2)
ggarrange(p7_New,p8_New,nrow = 2)
```

>>>>

# OSMAC
load(here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))

@@
